Template notebook for validating cell type assignments for an individual library in SCPCP000015

### 2025-01-24 analyses/cell-type-ewings/template_notebooks/celltype-exploration.Rmd
Apply suggestions from code review
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>
some minor review responses

1. Ensure that you have a local copy of the results from `aucell-singler-annotation.sh`, `evaluate-clusters.sh` and `run-aucell-ews-signatures.sh` saved to `results`. 
2. Copy the contents of this notebook to a new notebook titled `<library_id>_celltype-exploration.Rmd` and save in `exploratory_analysis/final_annotation_notebooks`. 
3. Replace the `sample_id` and `library_id` with the correct IDs in the `params` list. 
4. Optionally, you may choose to update the choices for clustering based on the results from `evaluate-clusters.sh`. 
All clusters used will be calculated with the Leiden algorithm and the modularity objective function. 
To modify the nearest neighbors (default: 20) and resolution (default: 0.5) chosen use the `cluster_nn` and `cluster_res` params. 
5. Run through the notebook and update any sections of the notebook marked with `**Manual exploration**`. 
6. Render the completed notebook which will produce the rendered `html` file and a TSV with cell type annotations for that library.

@@

# calculate gene set means for each cell type/cell state
cell_types <- unique(all_markers_df$cell_type)

@@

## Re-cluster tumor cells **Manual exploration**

@@

## Additional exploration **Manual exploration**

@@

## Validate final tumor and normal annotation **Manual exploration**

@@

## Prepare annotations **Manual exploration**

>>>>

1. Ensure that you have a local copy of the results from `aucell-singler-annotation.sh`, `evaluate-clusters.sh` and `run-aucell-ews-signatures.sh` saved to `results`. 
2. Copy the contents of this notebook to a new notebook titled `<library_id>_celltype-exploration.Rmd` and save in `exploratory_analysis/final_annotation_notebooks`. 
3. Update the `title` in the `yaml` section and replace the `sample_id` and `library_id` with the correct IDs in the `params` list. 
4. Optionally, you may choose to update the choices for clustering based on the results from `evaluate-clusters.sh`. 
All clusters used will be calculated with the Leiden algorithm and the modularity objective function. 
To modify the nearest neighbors (default: 20) and resolution (default: 0.5) chosen use the `cluster_nn` and `cluster_res` params. 
5. Run through the notebook and update any sections of the notebook marked with `**Manual exploration**`. 
6. Render the completed notebook which will produce the rendered `html` file and a TSV with cell type annotations for that library.

@@

cell_types <- unique(all_markers_df$cell_type)

@@

## Re-cluster tumor cells {.manual-exploration}

@@

## Additional exploration {.manual-exploration}

@@

## Validate final tumor and normal annotation {.manual-exploration}

@@

## Prepare annotations {.manual-exploration}
